\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \large \textbf{\textsc{#1}}}
    \vspace*{-6pt} \lineunder
    \vspace*{4pt}
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
%\vspace*{-10pt}
\begin{center}
    {\Huge \scshape \textbf{Matthew Berger}}\\
    \vspace*{4pt}
    Reno, NV $\cdot$ matthewjordanberger@gmail.com $\cdot$ 775.357.7884 $\cdot$ matthewjberger.xyz/portfolio\\
    \vspace*{-4pt}
\end{center}

%==== Experience ====%
\header{Work Experience}

\textbf{Scientific Games} \hfill Reno, NV\\
\textit{Software Engineer} \hfill July 2019 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Collaborated with remote engineers to integrate TextMeshPro into a Unity-based production casino game development framework.
	\item Assessed and quickly resolved batches of defects that were crucial to the release of major games.
\end{itemize}
\textbf{Hamilton Robotics} \hfill Reno, NV\\
\textit{Software Engineer} \hfill December 2017 - July 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Designed and built safety-critical software in a cross-disciplinary environment that calibrates and operates liquid-handling medical robots.
	\item Reduced development time for new calibration routines from two months to less than two weeks by consolidating multiple applications into a single GUI and reusable-plugin framework.
	\item Decreased development environment setup from a day to a few clicks by creating a bootstrapper that installs dependencies and configures settings on a Windows virtual machine.
	\item Worked directly with Hamilton\textquotesingle{}s largest OEM customer to architect an application that commands the firmware in their robots for rapidly diagnosing and resolving mechanical issues.
	\item Mentored new hires and interns on team processes and coding practices.
\end{itemize}
\textbf{Hamilton Robotics} \hfill Reno, NV\\
\textit{Software Engineering Intern} \hfill October 2014 - December 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Decreased time spent quality testing robots by more than a week per robot by automating the process of gravimetric analysis.
	\item Saved developers hours of time per day on common tasks by creating a suite of in-house tools.
	\item Improved instrument sales by creating software adapters for both SiLA and non-SiLA compliant devices through collaboration with third-party device manufacturers.
\end{itemize}
\textbf{Washoe REOC} \hfill Reno, NV\\
\textit{Software Engineer (Contract)} \hfill October 2014 - May 2016\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Created a SQL database and web application for emergency response teams to quickly search local subject matter expert contact information.
\end{itemize}

\header{Skills}
\begingroup
\setlength{\tabcolsep}{5pt} % Default value: 6pt
\renewcommand{\arraystretch}{1.1} % Default value: 1
\begin{tabular}{ l l }
	Languages:            & C\#, C++, Rust, Powershell, Python, Bash, Ruby, Javascript, Vimscript  \strut  \\
	DevOps:               & Git, TFS, Perforce, JIRA, Swarm, Confluence, Scoop, Cmake, Premake \strut      \\
	3D Graphics:          & OpenGL, Vulkan, GLSL, RenderDoc, Unity, SDL2, Assimp, Bullet, Ogre3D \strut    \\
	Linux:                & Linux CLI, SSH, Arch,  Systemd, Ubuntu, Fish, Vim, Emacs   \strut              \\
	Web Development:      & ASP.NET, MVC, IIS, Razor, Jinja, Flask, Jekyll, WASM, HTML  \strut   \\
	Desktop Applications: & WPF, MVVM, XAML, MEF, MahApps Metro, MvvmLight, WiX Toolset \strut             \\
	Mathematics:          & Linear algebra, Geometry, Trigonometry, Multivariable Calculus \strut          \\          
	Other:                & JSON, XML, Markdown, SiLA, Pester, YAML, LaTeX, GDB, Wireshark \strut            \\
\end{tabular}
\endgroup
\vspace{1mm}

%==== Education ====%
\header{Education}
\textbf{University of Nevada, Reno}\hfill Reno, NV\\
BS Computer Science and Engineering (Minor in Mathematics) \hfill August 2013 - Dec 2017\\
\vspace{2mm}

\header{Personal Projects}
{\textbf{DragonGlass}} {\sl Vulkan, Rust, GLSL/SPIR-V} \hfill https://github.com/matthewjberger/dragonglass\\
A cross-platform gltf scene renderer.\\
\vspace*{2mm}
{\textbf{Superbible}} {\sl OpenGL, Rust, GLSL} \hfill https://github.com/matthewjberger/superbible\\
A rust port of the OpenGL superbible.\\
\vspace*{2mm}
{\textbf{Iceberg3D}} {\sl C++, CMake, OpenGL, GLSL} \hfill https://github.com/matthewjberger/Iceberg3D\\
A small, structured game engine.\\
\vspace*{2mm}

\end{document}